Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
checking closed string paragraph
bullets

Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
each dg Lie algebra $\fg$ has an enveloping $\EE_n$ algebra $\UU_n\fg$, for every $n$, 
so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
Building on prior work \cite{BD, AF} [Owen's thesis?], 
Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $\EE_n$ algebra. 
Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
\begin{enumerate}
\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
\end{enumerate}
\owen{And keep going just a little.}
%
%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\fgl_\infty(A)$, where $A$ is a dg algebra. Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
%
%We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
%
%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\fgl_N(A)$, for a dg associative algebra $A$. Since the enveloping $\EE_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent. From this point of view, one can think of our main result as an $\EE_n$ generalization of the LQT theorem. We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.

@@

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the enveloping $\EE_n$ algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

@@

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.

@@

This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
$\cliels (\fg \otimes \Omega^\bu_c(U))$ to each open $U \subset \RR$.

@@

When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.

@@

The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
Indeed,
\begin{align*}
\int_{S^{n-1}}\UU_n\fg 
&\simeq \cliels(\Omega^\bu_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
&\simeq \cliels(\Omega^\bu_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
\end{align*}
because $(n-1)$-sphere is formal over the rationals (or reals). 
We thus see that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^*(S^{n-1}) \otimes \fg)
\]
The cohomology of the $(n-1)$-sphere is 
\[
R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
\] 
where $|\epsilon_{n-1}| = n-1$.
Since $\UU_1 (H^*(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
we find that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq U(\fg \otimes R_n)
\]
as $E_1$ algebras.
Recall as well that $\UU_n \fg$ is quasi-isomorphic to $\Sym(\fg[1-n])$ as cochain complexes.

@@

\begin{proof}[Proof of Proposition~\ref{prp: z commutes with int}]
The key fact is a simple consequence of the K\"unneth theorem in the setting of de Rham forms.
Let $S$ be the closed $n-k$-dimensional manifold of the proposition,
and let $V$ be an arbitrary manifold without boundary.
Then there is a canonical map
\[
\Omega^\bu(V) \otimes \Omega^\bu(S) \to \Omega^\bu(V \times S),
\]
by wedge product after pulling back along the two projection maps.
It is a quasi-isomorphism, by K\"unneth.
Similarly, the canonical map
\[
\Omega_c^*(V) \otimes \Omega^\bu(S) \to \Omega_c^*(V \times S),
\]
is a quasi-isomorphism, as $S$ is compact.

Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
\begin{align*}
\Omega^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
\Omega_c^*(V) \otimes \fg_S &\xto{\simeq} \Omega_c^*(V \times S) \otimes \fg 
\end{align*}
and hence a quasi-isomorphism
\[
\bU_k \fg_S \xto{\simeq} \int_S \bU_n \fg
\]
of factorization algebras.

@@

Consider first the case $n=1$ and $B = U \fg$. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as 
\[
\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad}).
\] 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section~\ref{??}.

@@

Let $\Cyc_*(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
A key theorem --- one of the original motivations for cyclic homology --- is the Loday-Quillen-Tsygan (LQT) theorem \cite{},
which provides an explicit quasi-isomorphism
\begin{equation}
\label{eqn: LQT}
\cliels(\fgl_\infty(A)) \xto{\simeq} \Sym(\Cyc_*(A)[1])
\end{equation}
for any unital dg associative algebra~$A$.
A similar result \cite{} holds when we replace $\fgl_N$ by $\frak{so}_N$ or $\frak{sp}_N$, with
\[
\label{eqn: LQT}
\cliels({\frak{so}}_\infty(A)) \xto{\simeq} \Sym(\Dih_*(A)[1]),
\]
with $\Dih_*$ denoting the dihedral chains.
Note that one can use either $\frak{so}_N$ or $\frak{sp}_N$ on the left hand side.

@@

Another key theorem, due to Jones \cite{} for cyclic chains and extend to dihedral chains by Ungheretti \cite{},
is that
\[
\Cyc_*(\Omega^*(M)) \simeq \Omega^*(LM/^h S^1)
\]
for a simply connected manifold $M$, 
where $LM/^h S^1$ denotes the homotopy quotient of the free loop space $LM$ under the canonical rotation action on loops,
and where we mean some model of cochains on the right hand side.
In other words, the right hand side is the $S^1$-equivariant cochains of the free loop space.
(This result holds, more generally, for a simply connected topological space of finite type, so long as one uses an appropriate model of cochains of the space, 
but we focus here on manifolds.)

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\begin{align*}
\int_M \UU_n(\frak{gl}_\infty)
&\simeq \cliels(\Omega^*(M) \otimes \fgl_\infty) \\
&\simeq \Sym(\Cyc_*(\Omega^*(M))[1]) \\
&\simeq \Sym(\Omega^*(LM/^h S^1))[1])).
\end{align*}
\end{lmm}

@@

This kind of result is especially interesting from the perspective of physics, 
as a kind of topological gauge/string duality.
In Section~\ref{sec: TFT} we explain how $\UU_n(\fgl_\infty)$ can be understood as the {\em quantum observables} of a gauge theory for the Lie algebra $\fgl_\infty$.
In this sense, the left hand side of the lemma $\int_M \UU_n(\frak{gl}_\infty)$ describes the global quantum observables over the manifold $M$.
On the right hand side, we see the cyclic loop space of $M$,
which arises naturally as the configuration space of a closed string theory with target~$M$.
Indeed, those familiar with closed string field theory will recognize the right hand side as related to the ``Fock space'' of such a theory.
\owen{Check me, Bri-guy.}

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\[
\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^*(LM/^h S^1))[1])))
\]
where the left hand side is the factorization homology of $\EE_n$ center ${\frak Z}_n(\fgl_\infty)$ and the right hand side is the $\EE_0$ center of the factorization homology of~$\UU_n \fgl_\infty$.
\end{lmm}

@@

We will use the following cochain maps defined at the level of differential forms in our constructions.
For an open set $V \subset M$ let $\int_{\RR_{>0}}$
(or $\int_{\RR_{\geq 0}}$)
be the map which integrates a compactly supported form on $V \times \RR_{> 0}$ or ($V \times \RR_{\geq 0}$) along $\RR_{> 0}$ (or $\RR_{\geq 0}$).
This map is a quasi-isomorphism for any $U$ and, in fact, admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR_{\geq 0}$ of mass $1$ and define
\[
r_\phi : \Omega^*_c(U) [1] \to \Omega^*_c (U \times \RR_{\geq 0})
\]
by $r_\phi (\alpha) = \pi^*\alpha \wedge \phi \, \d t$.

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega^* (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega^*_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which is defined on basic elements as follows.
On linear elements of the form $G : k \to \fg \otimes \Omega^\bu_c (V \times \RR_{>0})[2]$ the element $I^\circ(G)$ is given by the composition
\[
k \xto{G} \fg \otimes \Omega^\bu_c (V \times \RR_{>0})[2] \xto{1 \otimes \int_{\RR_{> 0}}} \fg \otimes \Omega^\bu_c(V) [1] .
\]
On linear elements of the form $F : \fg \otimes \Omega^\bu(V \times \RR_{>0})[1] \to k$ the element $I^{\circ} (F)$ is the composition
\[
\fg \otimes \Omega^\bu(V) [1] \xto{\pi^*} \fg \otimes \Omega^\bu(V \times \RR_{>0}) [1] \xto{F} k  .
\]

@@

\end{document}
We call $\ev_f$ the 
$g: Sym(\fg \otimes \Omega (U_J) [1]) \longrightarrow B(U_J) $
let $f\otimes X  $ be an 
element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)$.  
Let

@@

Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^* \to B$.
The unital factorization algebra is given, for any open $U$, by $k(U)=k$.

which gives us,  for any integer $n$, maps 
\begin{multline}
 Sym^n\big(\fg \otimes \Omega^\bu_c(U)[1]\big) \otimes Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] ,B(U)\big) \\
 \stackrel{\Delta \otimes id}\longrightarrow 
 \bigoplus_{q} Sym^{n-q}\big(\fg \otimes \Omega^\bu_c(U)[1]\big) \otimes  Sym^q\big(\fg \otimes \Omega^\bu_c(U)[1]\big) 
 \otimes Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] , B(U)\big)
 \\ 
 \stackrel{\id \otimes ev}\longrightarrow Sym^{n-p}\big(\fg \otimes \Omega^\bu_c(U)\big) \otimes B(U)  \hookrightarrow
 \cliels\big(\fg \otimes \Omega_c^*(U), B(U) \big) 
\end{multline}

>>>>

Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
each dg Lie algebra $\fg$ has an enveloping $\EE_n$ algebra $\UU_n\fg$, for every $n$, 
so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
Building on prior work \cite{BD, AF} [Owen's thesis?], 
Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $\EE_n$ algebra. 
Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
\begin{enumerate}
\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^\bu(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
\end{enumerate}
\owen{And keep going just a little.}
%
%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\fgl_\infty(A)$, where $A$ is a dg algebra. Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
%
%We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
%
%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\fgl_N(A)$, for a dg associative algebra $A$. Since the enveloping $\EE_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent. From this point of view, one can think of our main result as an $\EE_n$ generalization of the LQT theorem. We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.

@@

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the enveloping $\EE_n$ algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^\bu(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

@@

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^\bu \otimes \fg) \to \cliels(\Omega_c^\bu \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^\bu \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.

@@

This result generalizes the fact that $\Hoch^\bu(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
$\cliels (\fg \otimes \Omega^\bu_c(U))$ to each open $U \subset \RR$.

@@

When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^\bu(A,B_f)$,
where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.

@@

The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
Indeed,
\begin{align*}
\int_{S^{n-1}}\UU_n\fg 
&\simeq \cliels(\Omega^\bu_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
&\simeq \cliels(\Omega^\bu_c(\RR_{> 0}) \otimes H^\bu(S^{n-1}) \otimes \fg)
\end{align*}
because $(n-1)$-sphere is formal over the rationals (or reals). 
We thus see that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^\bu(S^{n-1}) \otimes \fg)
\]
The cohomology of the $(n-1)$-sphere is 
\[
R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
\] 
where $|\epsilon_{n-1}| = n-1$.
Since $\UU_1 (H^\bu(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
we find that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq U(\fg \otimes R_n)
\]
as $E_1$ algebras.
Recall as well that $\UU_n \fg$ is quasi-isomorphic to $\Sym(\fg[1-n])$ as cochain complexes.

@@

\begin{proof}[Proof of Proposition~\ref{prp: z commutes with int}]
The key fact is a simple consequence of the K\"unneth theorem in the setting of de Rham forms.
Let $S$ be the closed $n-k$-dimensional manifold of the proposition,
and let $V$ be an arbitrary manifold without boundary.
Then there is a canonical map
\[
\Omega^\bu(V) \otimes \Omega^\bu(S) \to \Omega^\bu(V \times S),
\]
by wedge product after pulling back along the two projection maps.
It is a quasi-isomorphism, by K\"unneth.
Similarly, the canonical map
\[
\Omega_c^\bu(V) \otimes \Omega^\bu(S) \to \Omega_c^\bu(V \times S),
\]
is a quasi-isomorphism, as $S$ is compact.

Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
\begin{align*}
\Omega^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
\Omega_c^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega_c^\bu(V \times S) \otimes \fg 
\end{align*}
and hence a quasi-isomorphism
\[
\bU_k \fg_S \xto{\simeq} \int_S \bU_n \fg
\]
of factorization algebras.

@@

Consider first the case $n=1$ and $B = U \fg$. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as 
\[
\Hoch^\bu(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad}).
\] 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section~\ref{??}.

@@

Let $\Cyc_\bu(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
A key theorem --- one of the original motivations for cyclic homology --- is the Loday-Quillen-Tsygan (LQT) theorem \cite{},
which provides an explicit quasi-isomorphism
\begin{equation}
\label{eqn: LQT}
\cliels(\fgl_\infty(A)) \xto{\simeq} \Sym(\Cyc_\bu(A)[1])
\end{equation}
for any unital dg associative algebra~$A$.
A similar result \cite{} holds when we replace $\fgl_N$ by $\frak{so}_N$ or $\frak{sp}_N$, with
\[
\label{eqn: LQT}
\cliels({\frak{so}}_\infty(A)) \xto{\simeq} \Sym(\Dih_\bu(A)[1]),
\]
with $\Dih_\bu$ denoting the dihedral chains.
Note that one can use either $\frak{so}_N$ or $\frak{sp}_N$ on the left hand side.

@@

Another key theorem, due to Jones \cite{} for cyclic chains and extend to dihedral chains by Ungheretti \cite{},
is that
\[
\Cyc_\bu(\Omega^\bu(M)) \simeq \Omega^\bu(LM/^h S^1)
\]
for a simply connected manifold $M$, 
where $LM/^h S^1$ denotes the homotopy quotient of the free loop space $LM$ under the canonical rotation action on loops,
and where we mean some model of cochains on the right hand side.
In other words, the right hand side is the $S^1$-equivariant cochains of the free loop space.
(This result holds, more generally, for a simply connected topological space of finite type, so long as one uses an appropriate model of cochains of the space, 
but we focus here on manifolds.)

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\begin{align*}
\int_M \UU_n(\frak{gl}_\infty)
&\simeq \cliels(\Omega^\bu(M) \otimes \fgl_\infty) \\
&\simeq \Sym(\Cyc_\bu(\Omega^\bu(M))[1]) \\
&\simeq \Sym(\Omega^\bu(LM/^h S^1))[1])).
\end{align*}
\end{lmm}

@@

This kind of result is especially interesting from the perspective of physics, 
as a kind of topological gauge/string duality.
In Section~\ref{sec: TFT} we explain how $\UU_n(\fgl_\infty)$ can be understood as the {\em quantum observables} of a gauge theory for the Lie algebra $\fgl_\infty$.
In this sense, the left hand side of the lemma $\int_M \UU_n(\frak{gl}_\infty)$ describes the global quantum observables over the manifold $M$.
On the right hand side, we see the cyclic loop space of $M$,
which arises naturally as the configuration space of a closed string theory with target~$M$.
Indeed, those familiar with closed string field theory will recognize the right hand side as related to the ``Fock space'' of such a theory.

@@

\begin{lmm}
For a closed $n$-dimensional manifold~$M$, 
\[
\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^\bu(LM/^h S^1))[1])))
\]
where the left hand side is the factorization homology of $\EE_n$ center ${\frak Z}_n(\fgl_\infty)$ and the right hand side is the $\EE_0$ center of the factorization homology of~$\UU_n \fgl_\infty$.
\end{lmm}

@@

We will use the following cochain maps defined at the level of differential forms in our constructions.
For an open set $V \subset M$ let $\int_{\RR_{>0}}$
(or $\int_{\RR_{\geq 0}}$)
be the map which integrates a compactly supported form on $V \times \RR_{> 0}$ or ($V \times \RR_{\geq 0}$) along $\RR_{> 0}$ (or $\RR_{\geq 0}$).
This map is a quasi-isomorphism for any $U$ and, in fact, admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR_{\geq 0}$ of mass $1$ and define
\[
r_\phi : \Omega^\bu_c(U) [1] \to \Omega^\bu_c (U \times \RR_{\geq 0})
\]
by $r_\phi (\alpha) = \pi^*\alpha \wedge \phi \, \d t$.

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega^\bu (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which is defined on basic elements as follows.
On linear elements of the form $G : k \to \fg \otimes \Omega^\bu_c (V \times \RR_{>0})[2]$ the element $I^\circ(G)$ is given by the composition
\[
k \xto{G} \fg \otimes \Omega^\bu_c (V \times \RR_{>0})[2] \xto{1 \otimes \int_{\RR_{> 0}}} \fg \otimes \Omega^\bu_c(V) [1] .
\]
On linear elements of the form $F : \fg \otimes \Omega^\bu(V \times \RR_{>0})[1] \to k$ the element $I^{\circ} (F)$ is the composition
\[
\fg \otimes \Omega^\bu(V) [1] \xto{\pi^*} \fg \otimes \Omega^\bu(V \times \RR_{>0}) [1] \xto{F} k  .
\]

@@

\end{document}
We call $\ev_f$ the 
$g: Sym(\fg \otimes \Omega (U_J) [1]) \longrightarrow B(U_J) $
let $f\otimes X  $ be an 
element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^\bu \big)$.  
Let

@@

Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^\bu \to B$.
The unital factorization algebra is given, for any open $U$, by $k(U)=k$.

which gives us,  for any integer $n$, maps 
\begin{multline}
 Sym^n\big(\fg \otimes \Omega^\bu_c(U)[1]\big) \otimes Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] ,B(U)\big) \\
 \stackrel{\Delta \otimes id}\longrightarrow 
 \bigoplus_{q} Sym^{n-q}\big(\fg \otimes \Omega^\bu_c(U)[1]\big) \otimes  Sym^q\big(\fg \otimes \Omega^\bu_c(U)[1]\big) 
 \otimes Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] , B(U)\big)
 \\ 
 \stackrel{\id \otimes ev}\longrightarrow Sym^{n-p}\big(\fg \otimes \Omega^\bu_c(U)\big) \otimes B(U)  \hookrightarrow
 \cliels\big(\fg \otimes \Omega_c^\bu(U), B(U) \big) 
\end{multline}
